---
title: "ggplot_Palmer Penguins"
author: "Darrell D"
date: "2022-09-02"
output: html_document
---

## Setting up my environment
Notes: Setting up my R environment by loading and installing packages tidyverse and palmerpegnuins

```{r loading packages}
install.packages("tidyverse")
install.packages("palmerpenguins")
library(tidyverse)
library(palmerpenguins)
```

## Visualization
Here we will go thtough series of visualization

## Flipper and body mass in purple
We plot Flipper length and Body mass in color

```{r viz flipper vs body mass in purple}
ggplot(data=penguins, aes(x=flipper_length_mm,y=body_mass_g)) + 
  geom_point(color="purple")
```

## Flipper and body mass by Species
We Plot Flipper length and Body mass by Species

```{r by species}
ggplot(data=penguins, aes(x=flipper_length_mm,y=body_mass_g)) + 
  geom_point(aes(shapes=species))
```

## Flipper and body mass by sex and species
We plot Flipper length and Body mass by Sex and Species

```{r by species and sex}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) + 
  geom_point(aes(color=species)) + 
  facet_grid(sex~species)

```

